RNA-seq from 4 cell populations

### 2020-08-21 deconvolution/fans4/molec_profiling.Rmd
Initial commit

nEXP_OBJ = File(file, 
                name = 'FANS4 reference panel: log2CPM', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, 
                    executed = thisFile)

@@

nEXP_OBJ = File(file, 
                name = 'FANS4 reference panel: log2CPM standard error', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, 
                    executed = thisFile)

@@

nEXP_OBJ = File(file, 
                name = 'FANS4 reference panel: full counts', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, 
                    executed = thisFile)

@@

nEXP_OBJ = File(file, 
                name = 'FANS4 reference panel: metadata', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, 
                    executed = thisFile)

>>>>

nEXP_OBJ = File(file, 
                name = 'FANS4 reference panel - log2CPM', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, 
                    executed = thisFile)

@@

nEXP_OBJ = File(file, 
                name = 'FANS4 reference panel - log2CPM standard error', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, 
                    executed = thisFile)

@@

nEXP_OBJ = File(file, 
                name = 'FANS4 reference panel - full counts', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, 
                    executed = thisFile)

@@

nEXP_OBJ = File(file, 
                name = 'FANS4 reference panel - metadata', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, 
                    executed = thisFile)
